---
title: "Adding Logos"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Adding Logos}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 6,
  fig.asp = 0.618,
  out.width = '70%'
)
```

## Overview

In order to add a logo you should create your plot, save it, and then use `add_logo()`.
The function takes on six arguments:

-   `plot_path`: url or local file for the plot

-   `logo_path`: url, local file for the plot or one of the built in logos.

-   `logo_position`: Can be 'top left', 'top right', 'bottom left', and 'bottom right'.
    As per the Brookings style guide, the default logo position is 'bottom right'.

-   `logo_scale`: The portion of the plot width the logo should occupy.
    The default is 5 which means that the logo will be 1/5th of the plot width.

-   `height_padding`: Control the y axis position of a logo by specifying the padding proportion.
    Default is 4.5% padding.

-   `width_padding`: Control the x axis position of a logo by specifying the padding proportion.
    Default is 1% padding.

Currently, the available built in logos are:

+----------------------------------------------+--------------------------------+
| Program/Center                               | Abbreviation                   |
+:=============================================+:===============================+
| Brookings                                    | 'brookings'                    |
+----------------------------------------------+--------------------------------+
| Economic Studies                             | 'es'                           |
+----------------------------------------------+--------------------------------+
| Government Studies                           | 'gs'                           |
+----------------------------------------------+--------------------------------+
| Foreign Policy                               | 'fp'                           |
+----------------------------------------------+--------------------------------+
| Metro                                        | 'metro'                        |
+----------------------------------------------+--------------------------------+
| Global                                       | 'global'                       |
+----------------------------------------------+--------------------------------+
| Bass Initiative                              | 'bi'                           |
+----------------------------------------------+--------------------------------+
| Brown Center                                 | 'bc'                           |
+----------------------------------------------+--------------------------------+
| China Center                                 | 'cc'                           |
+----------------------------------------------+--------------------------------+
| Center for Children and Families             | 'ccf'                          |
+----------------------------------------------+--------------------------------+
| Center for East Asia Policy Studies          | 'ceaps'                        |
+----------------------------------------------+--------------------------------+
| Center for Effective Public Management       | 'cepm'                         |
+----------------------------------------------+--------------------------------+
| Center for Health Policy                     | 'chp'                          |
+----------------------------------------------+--------------------------------+
| Center for Middle East Policy                | 'cmep'                         |
+----------------------------------------------+--------------------------------+
| Center for Sustainable Development           | 'csd'                          |
+----------------------------------------------+--------------------------------+
| Center for Technology Innovation             | 'cti'                          |
+----------------------------------------------+--------------------------------+
| Center for Universal Education               | 'cue'                          |
+----------------------------------------------+--------------------------------+
| Center on United States and Europe           | 'cuse'                         |
+----------------------------------------------+--------------------------------+
| Center on Regulation and Markets             | 'crm'                          |
+----------------------------------------------+--------------------------------+
| Doha Center                                  | 'doha'                         |
+----------------------------------------------+--------------------------------+
| Hutchins Center                              | 'hc'                           |
+----------------------------------------------+--------------------------------+
| Brookings-Tsinghua Center for Public Policy  | 'tsinghua'                     |
+----------------------------------------------+--------------------------------+

For more information on how this function works, please read Tom Mock's fantastic blog post on [how to add a logo to your plot](https://themockup.blog/posts/2019-01-09-add-a-logo-to-your-plot/).
`ggbrookings::add_logo()` builds off of the function described in the article with some minor modifications.

## Example

We start by creating a plot and using `ggsave()` to save it.

```{r, eval = TRUE}
librarian::shelf(tidyverse, ggbrookings, palmerpenguins)
theme_set(theme_brookings())
p1 <-
  ggplot(data = penguins, aes(x = flipper_length_mm)) +
  geom_histogram(aes(fill = species),
                 alpha = 0.5,
                 position = "identity",
                 bins = 30) +
  scale_fill_brookings(palette = "semantic3") +
  labs(x = "Flipper length (mm)",
       y = "Frequency",
       title = "Penguin flipper lengths",
       caption = '**Source:** Palmer Penguins',
       tag = 'Figure 1')

ggsave("penguins.png", p1, dpi=300, height=3.7, width=6, units="in")



```

Finally, to add a logo call:

```{r, out.width='70%', fig.align='center'}

add_logo('penguins.png', logo_path = 'brookings', 'bottom right', 5)
```
