---
title: "Brookings Palettes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Brookings Palettes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE,
  comment = "#>"
)
```

```{r setup}
library(ggbrookings)
```

You can check out all the colors for each palette by running     `brookings_view_palette('name_of_palette')`. The colors in some of these palettes may still change from feedback and further experimentation. Some examples below:

## Brand 
The brand palette is the default for the `scale_brookings_` functions. Use colors from the brand palette whenever possible.
```{r}

brookings_view_palette('brand1')
brookings_view_palette('brand2')
```

## Analogous
Different shades of the same hue, or of similar hues can be used when the associated values are related.
```{r}
brookings_view_palette('analogous1')
brookings_view_palette('analogous2')
```

## Contrasting
Colors on the opposite ends of the spectrum. Use Brookings Blue with Secondary colors.
```{r}
brookings_view_palette('contrasting1')
brookings_view_palette('contrasting2')
```

## Semantic
Where applicable, use colors that are associated with certain concepts. For example, `semantic3` could show subsets of gender data (female, male and other).
```{r}
brookings_view_palette('semantic1')
brookings_view_palette('semantic2')
brookings_view_palette('semantic3')

```

## Positive and negative
Shows pros, cons and neutral, or positive, negative and neutral data.
```{r}
brookings_view_palette('pos_neg1')
brookings_view_palette('pos_neg2')
```

## Political
Use red and blue of similar intensity to represent data related to political parties in the US. Yellow in political3 and political4 represents ‘Independent’ category
```{r}
brookings_view_palette('political1')
brookings_view_palette('political2')
brookings_view_palette('political3')
brookings_view_palette('political4')
```

## Categorical

Distinguish discrete categories of data that do not have an inherent ordering. This palette uses distinct hues of visually similar brightness and saturation to avoid creating a sense of order or priority. A maximum of 6 categorical colors are provided as it becomes difficult for people to distinguish between hues after 5-8 colors. If more than 6 colors are needed, consider alternative solutions such as grouping some categories or using alternative visual cues. 
```{r}
brookings_view_palette('categorical')
```

## Sequential
Sequential palettes are used to show an inherent order or variations in numeric values. Light colors typically indicate low values and darker or brighter colors  indicate high values.
```{r}
brookings_view_palette('sequential1')
```

In addition to variations in lightness, we can also use two distinct hues to give more contrast. 
```{r}
brookings_view_palette('sequential2')
```
 
## Diverging 
Diverging palettes are useful when dealing with negative and positive values or a range of values that have two extremes with a baseline central value, like zero. The Brookings diverging palette should uses two distinct hues of similar brightness and saturation with a neutral color in the middle. Using a discrete set of colors with evenly distributed gradation can improve clarity of values relative to a continuous palette. 
```{r}
brookings_view_palette('diverging')
```

## Miscellaneous 
A pleasing option using Brookings Blue and accent yellow.
```{r}
brookings_view_palette('misc')
```

